Summary Tables

### 2021-11-18 summary_tables.Rmd
Regen latam
Rename variables and add trip proportion for scenarios as well

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis')

@@

```{r}

@@

dat[[city]] <- io[[city]]$trip_scen_sets %>% mutate(scenario = case_when(
  scenario == "Scenario 1" ~ "PED_SC", 
  scenario == "Scenario 2" ~ "CYC_SC",
  scenario == "Scenario 3" ~ "CAR_SC",
  scenario == "Scenario 4" ~ "MOT_SC",
  scenario == "Scenario 5" ~ "BUS_SC",
  scenario == "Baseline" ~ "Baseline")) %>% group_by(scenario, trip_mode, trip_distance_cat) %>% summarise(n = dplyr::n()) %>% mutate(city = city) %>% filter(!(trip_mode %in% "truck"))

@@

    if (nrow(val) > 0){
      td$diff[i] <- val$n - td$n[i]
      td$prop[i] <- round(td$n[i] / val$n, 2)

@@

for(city in cities){
  print(city)
  df <- io[[city]]$trip_scen_sets
  u_trips <- df %>% dplyr::filter(scenario == "Baseline") %>% summarise(uid <- n_distinct(trip_id)) %>% as.numeric()
  td <- df %>% distinct(trip_id, scenario, .keep_all = T) %>% group_by(trip_mode, scenario) %>% summarise(p = round(dplyr::n() / u_trips * 100, 1)) %>% spread(key = trip_mode, value = p) %>% mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td <- as.data.frame(t(td))
  names(td) <- lapply(append('BASELINE', rownames(scen_prop)), as.character)
  td <- td[-1, ]
  x <- match(row.names(td), trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]

@@

  print(city)
  count_people <- round(sum(io[[city]]$demographic$population))
  td <- io[[city]]$true_dist %>% dplyr::filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, list(~round((.) * 365, 3)))
  #colnames(td)[3:7] <- rownames(scen_prop)
  colnames(td)[2:7] <- c("BASELINE", rownames(scen_prop))

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis', warning = F)

@@

```{r warning=FALSE, echo=F, message=FALSE}

@@

dat[[city]] <- io[[city]]$trip_scen_sets %>% mutate(scenario = case_when(
  scenario == "Scenario 1" ~ "PED_SC", 
  scenario == "Scenario 2" ~ "CYC_SC",
  scenario == "Scenario 3" ~ "CAR_SC",
  scenario == "Scenario 4" ~ "MOT_SC",
  scenario == "Scenario 5" ~ "BUS_SC",
  scenario == "Baseline" ~ "Baseline")) %>% group_by(scenario, trip_mode, trip_distance_cat) %>% summarise(n = dplyr::n(), dist = sum(trip_distance, na.rm = T)) %>% mutate(city = city)

@@

    if (nrow(val) > 0){
      td$diff[i] <- val$n - td$n[i]
      td$trip_prop[i] <- round(td$n[i] / val$n, 2)
      td$dist_prop[i] <- round(td$dist[i] / val$dist, 2)

@@

for(city in cities){
  df <- io[[city]]$trip_scen_sets
  u_trips <- df %>% dplyr::filter(scenario == "Baseline") %>% summarise(uid <- n_distinct(trip_id)) %>% as.numeric()
  td <- df %>% distinct(trip_id, scenario, .keep_all = T) %>% group_by(trip_mode, scenario) %>% summarise(p = round(dplyr::n() / u_trips * 100, 1)) %>% spread(key = trip_mode, value = p) %>% mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td <- as.data.frame(t(td))
  names(td) <- lapply(append('BASELINE', rownames(scen_prop)), as.character)
  td <- td[-1, ]
  x <- match(row.names(td), trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]

@@

  count_people <- round(sum(io[[city]]$demographic$population))
  td <- io[[city]]$true_dist %>% dplyr::filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, list(~round((.) * 365, 3)))
  #colnames(td)[3:7] <- rownames(scen_prop)
  colnames(td)[2:7] <- c("BASELINE", rownames(scen_prop))
